### 2017-10-13 Gruba/03-fe.tex

\stitle{Step 5:} TF-IDF based similarity is calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
Go to \textbf{Step 7}.

@@

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$,
and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
Go to \textbf{Step 7}.

>>>>

\stitle{Step 5:} TF-IDF based similarity is calculated.
%For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined %as:
%\begin{equation}
%\label{eq:sim-tf1}
%sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
%\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
%Go to \textbf{Step 7}.

For example, the similarity of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as formula \ref{eq:sim-tf1}. Here $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion}, where $N_t$ is the word count in topic $t$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
\begin{equation}
\label{eq:sim-tf1}
%\cdot
sim(W_f, t) = VEC_{W_f} \cdot VEC_t
%\sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
\begin{equation}
\label{eq:sum-tf1}
%\cdot
VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i]
%\sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
\begin{equation}
\label{eq:sum-lexion}
%\cdot
VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j]
%\sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}

%and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$
%Go to \textbf{Step 7}.

@@

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
%Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined %as:
%\begin{equation}
%\label{eq:sim-tw1}
%sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
%\end{equation}
%%%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
%where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$,
%and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
%Go to \textbf{Step 7}.

Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = VEC_{W_w} \cdot VEC_t
\end{equation}
%%%where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$,
where $W_w$ is a set of $(w'_i, p'_i)$, $t$ covers each $c_j$, and $VEC_{W_w}$ can be obtained similarly as $VEC_{W_f}$.
